% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{resume}

\usepackage{hyperref}
\usepackage{microtype}

% For \email{ADDRESS}, links ADDRESS to the url mailto:ADDRESS
\providecommand*\email[1]{\href{mailto:#1}{#1}}
% Same as above, but pretty-prints ADDRESS in teletype fixed-width font
%\renewcommand*\email[1]{\href{mailto:#1}{\texttt{#1}}}

\begin{document}
\begin{tabular*}{7.15in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Dr. Boxun Zhang} & \texttt{+4915229402625} \\
Sr. Data Scientist at SoundCloud & \texttt{zhangboxun@gmail.com} \\
Ph.D. in Computer Science & \href{https://zhangboxun.github.io/}{\texttt{zhangboxun.github.io}} \\
Based in Berlin, Germany & \href{https://www.quora.com/profile/Boxun-Zhang}{\texttt{Quora}} \\
\end{tabular*}
\\
\begin{resume}

\section{\mysidestyle Profile}

I recently started working at SoundCloud as a senior data scientist. Previously, I worked
as a data scientists at Spotify on various topics: machine learning, user behavior measurement,
experimentation, and research collaboration. I obtained my PhD in Computer Science from Delft
University of Technology, the Netherlands, where I studied user behavior in Peer-to-Peer file
sharing systems.

\section{\mysidestyle Professional \\Experience}
\textbf{Senior Data Scientist} \hfill \textbf{May 2017 -- present} \vspace{0.75mm} \\%
\textsl{SoundCloud, Germany} \vspace{1.5mm} \\
\vspace{-4.5mm}\\
Research and develop models, tools, and datasets that are used by other data scientists.

\textbf{Data Scientist} \hfill \textbf{Mar. 2013 -- Feb. 2017} \vspace{0.75mm} \\%
\textsl{Spotify, Sweden} \vspace{1.5mm} \\
\vspace{-4.5mm}\\
Worked in various areas, including:
\begin{list2}
    \item Modeled user retention with machine learning techniques
    \item Measured and modeled user experience frictions in Spotify's mobile app
    \item Develope machine learning approach that reveals the cause of effect
        in A/B testing
    \item Developed a machine learning model that can predict A/B testing result
    \item Designed and developed the first user session dataset that was widely used
        within Spotify
    \item Built intra-session attribution model that associates streaming behavior
    to other types of user behaviors
    \item Built model that predicted the time it takes Spotify's Hadoop
    cluster (2,000+ nodes) to run out of storage capacity.
    \item Supported multiple product teams by designing and analyzing A/B tests
\end{list2}

\vspace{-2.5mm}\\

(Co)supervised PhD and MSc students for research projects:
\begin{list2}
    \item S. Magureanu: \emph{Online Learning of Optimally Diverse Rankings} (PhD internship)
    \item F. Michelinakis: \emph{Passive Mobile Bandwidth
    Classification Using Short Lived TCP Connections} (PhD internship)
    \item G. M{\"o}rtberg: \emph{Detection of Streaming Fraud} (MSc internship)
    \item M. H{\aa}stad: \emph{Evaluating Different Sessionization Methods in
    Music Streaming Context} (MSc thesis)
    \item E. Aalto: \emph{Learning Playlist Representations for Automatic Playlist
    Generation} (MSc thesis)
    \item T. Vasiloudis: \emph{Extending Recommendation Algorithms by Modeling
    User Context} (MSc thesis)
\end{list2}

\textbf{Research Intern} \hfill \textbf{Jan. 2012 -- May 2012} \vspace{0.75mm} \\%
\textsl{Spotify, Stockholm, Sweden} \vspace{1.5mm} \\
Investigated various aspects of user behavior in Spotify, such as arrival
patterns of user sessions and usage patterns of users with multiple
devices.

\textbf{Software Engineer} \hfill \textbf{Feb. 2006 -- Apr. 2008} \vspace{0.75mm} \\%
\textsl{International Air Transport Association, Beijing, China} \vspace{1.5mm} \\
Designed and developed web services for internal systems.

% Education
\section{\mysidestyle Education}
\textbf{Ph.D. in Computer Science} \hfill \textbf{May 2008 -- Jan. 2013} \vspace{0.75mm} \\%
\textsl{Delft University of Technology, Delft, the Netherlands} \vspace{-2.5mm} \\
\begin{list2}
    \item Thesis: Understanding Operation and User Behavior in Peer-to-Peer Systems
    \item Promotor: Prof.dr.ir. H.J. Sips
    \item Supervisor: Dr.ir. J.A. Pouwelse
\end{list2}
\vspace{-3mm}
I studied the system dynamics and user behaviors in Peer-to-Peer (P2P) systems
like BitTorrent, through empirical analysis and statistical modeling.
I was also one of the main contributors of
\href{http://p2pta.ewi.tudelft.nl/}{\texttt{P2P Trace Archive}} ---
one of the largest public data archives for P2P traces.

\newpage

\textbf{M.Sc. in Computer Science} \hfill \textbf{Aug. 2004 -- Feb. 2016} \vspace{0.75mm} \\%
\textsl{Royal Institute of Technology, Stockholm, Sweden} \vspace{-2.5mm} \\
\begin{list2}
    \item Thesis: Implementation of Agora System (multi-agent systems)
    \item Supervisor: Prof. Mihhail Matskin
\end{list2}\vspace{-1.5mm}

\textbf{B.Sc. in Computer Science} \hfill \textbf{Sept. 2000 -- Jun. 2004} \vspace{0.75mm} \\%
\textsl{Royal Institute of Technology, Stockholm, Sweden} \vspace{-2.5mm} \\
\begin{list2}
    \item Thesis: Device Driver Development for Embedded Linux
    \item Supervisor: Dr. Zhongmei Ma
\end{list2}\vspace{-1.5mm}

\section{\mysidestyle Talks}
\href{http://www.slideshare.net/BoxunZhang/machine-learning-the-product}{\emph{Machine Learning the Product}}. Nordic Data Science Summit, 2016

\vspace{-3mm}
\href{https://www.kth.se/social/files/573d8d10f276545b25e543c9/guest_lecture_DD2476_2016_Boxun.pdf}{\emph{Introduction to Locality Sensitive Hashing}}.
Guest lecture for Search Engines and Information Retrieval Systems, KTH, 2016

\vspace{-3mm}
\href{http://softwareengineeringdaily.com/2015/12/11/data-science-at-spotify-with-boxun-zhang/}{\emph{Data Science at Spotify with Boxun Zhang}}.
Software Engineering Daily, 2015

\vspace{-3mm}
\href{http://linc.ucy.ac.cy/isocial/images/stories/Events/Crete_workshop/Speaker%20Slides/Speaker%20Slides/NOT%20FOR%20WEB%20music_recommendation_spotify.pdf}{\emph{Music Recommendation in Spotify}}.
Online Social Networks: Data Management and Privacy/Security workshop, 2015

\section{\mysidestyle Publications}
Stefan Magureanu, Alexandre Proutiere, Marcus, Isaksson, \textbf{Boxun Zhang}.
\textit{Online Learning of Optimally Diverse Rankings}. ACM SIGMETRICS, 2018 (accepted).

Foivos Michelinakis, Gunnar Kreitz, Riccardo Petrocco, \textbf{Boxun Zhang}, and Joerg
Widmer. \textit{Passive Mobile Bandwidth Classification Using Short Lived TCP
Connections}. IFIP WMNC, 2015.

\vspace{-2mm}
\textbf{Boxun Zhang}, Gunnar Kreitz, Marcus Isaksson, Javier Ubillos, Guido
Urdenata, Johan Pouwelse, and Dick Epema. \emph{Understanding User Behavior
in Spotify}. IEEE INFOCOM, 2013.

\vspace{-2mm}
\textbf{Boxun Zhang}, Alexandru Iosup, Johan Pouwelse, and Dick Epema.
\emph{Characterizing Flashcrowds in BitTorrent}. ICT.OPEN, 2012.
\emph{Best paper award of ASCI track}

\vspace{-2mm}
\textbf{Boxun Zhang}, Alexandru Iosup, Johan Pouwelse, and Dick Epema.
\emph{Identifying, Analyzing, and Modeling Flashcrowds in BitTorrent}. IEEE P2P Computing,
2011.

\vspace{-2mm}
\textbf{Boxun Zhang}, Alexandru Iosup, Johan Pouwelse, and Dick Epema. \emph{The
Peer-to-Peer Trace Archive: Design and Comparative Trace Analysis}. ACM CoNEXT
Student Workshop, 2010.

\vspace{-2mm}
\textbf{Boxun Zhang}, Alexandru Iosup, Johan Pouwelse, and Dick Epema.
\emph{Towards a Peer-to-Peer Trace Archive}. ASCI, 2010.

\vspace{-2mm}
\textbf{Boxun Zhang}, Alexandru Iosup, Johan Pouwelse, Dick Epema, and Henk
Sips. \emph{Sampling Bias in BitTorrent Measurements}. Euro-Par, 2010.

\vspace{-2mm}
\textbf{Boxun Zhang}, Alexandru Iosup, Johan Pouwelse, and Pawel Garbacki.
\textit{A Unified Format for Traces of Peer-to-Peer Systems}. LSAP, 2009.

\vspace{-2mm}
David Hales, Rameez Rahman, \textbf{Boxun Zhang}, Michel Meulpolder and Johan
Pouwelse. \textit{BitTorrent or BitCrunch: Evidence of a credit squeeze in
BitTorrent?}. COPS Workshop, 2009.

\vspace{-2mm}
Xuetao Niu, \textbf{Boxun Zhang}, and Mihhail Matskin. \textit{An Architecture
and System for Support of Cooperation in Multi-Agent Software Development}. SERP,
2007.


%\section{\mysidestyle Technical Reports}
%\textbf{Boxun Zhang}, Alexandru Iosup, Johan Pouwelse, and Dick Epema.
%\emph{Identifying, Analyzing, and Modeling Flashcrowds in BitTorrent}. Technical
%Report PDS-2010-009, Delft University of Technology.

%\vspace{-2mm}
%\textbf{Boxun Zhang}, Alexandru Iosup, and Dick Epema. \textit{The Peer-to-Peer
%Trace Archive: Design and Comparative Trace Analysis}. Technical Report PDS-2010-003,
%Delft University of Technology.

%\vspace{-2mm}
%\textbf{Boxun Zhang}, Alexandru Iosup, Johan Pouwelse, Dick Epema, and Henk Sips.
%\textit{On Assessing Measurement Accuracy in BitTorrent Peer-to-Peer File-Sharing
%Networks}. Technical Report PDS-2009-005, Delft University of Technology.

\section{\mysidestyle Skills}
\textbf{Programming}: Python, R, Scala, Java

\vspace{-3mm}
\textbf{Big data}: MapReduce, Spark, BigQuery, Hive, SQL

\vspace{-3mm}
\textbf{Data visualization}: ggplot2, Seaborn, Matplotlib, D3.js, Graphviz, Gnuplot


\section{\mysidestyle Languages}
English -- fluent/proficient in speaking, reading, and writing

\vspace{-3mm}

Chinese -- native speaker

%\section{\mysidestyle References}
%Available upon request

%\begin{tabular}{@{}p{7cm}p{7cm}}
%\textbf{Dr. Dick Epema} & \textbf{Dr. Alexandru Iosup} \\
%Associate Professor & Assistant Professor \\
%Parallel and Distributed Systems group, & Parallel and Distributed Systems group,\\
%EEMCS, Delft University of Technology, & EEMCS, Delft University of Technology,\\
%Mekelweg 4, 2628 CD, Delft, Netherlands & Mekelweg 4, 2628 CD, Delft, Netherlands\\
%phone: \texttt{+31-15-2783853} & phone: \texttt{+31-15-2784433}\\
%email: \texttt{D.H.J.Epema@.tudelft.nl} & email: \texttt{A.Iosup@tudelft.nl}    \\
%\end{tabular}

%\begin{tabular}{@{}p{7cm}p{7cm}}
%\textbf{Dr. Johan Pouwelse} & \\
%Assistant Professor & \\
%Parallel and Distributed Systems group, & \\
%EEMCS, Delft University of Technology, & \\
%Mekelweg 4, 2628 CD, Delft, Netherlands & \\
%phone: \texttt{+31-15-2782539} & \\
%email: \texttt{peer2peer@gmail.com} & \\
%\end{tabular}

\end{resume}
\end{document}

